Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-01-11 nips2015.tex
ENH: getting ready for arxiv

\subsection{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, $\sigma_h$ (unique and well-defined, by the  is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

>>>>

\subsection{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, denote by $\sigma_h$  the sequence of choices ((unique and well-defined, by the the ongoing perfect-recall asumption) from the root node, to --any node of-- $h$, ignoring the choices of the other players. \textit{perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices, and so $\sigma_h$ is well-defined. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.
